Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
minor fix.

We can categorize behaviors into two types: visible behaviors
and internal behaviors.
Visible behaviors are those which are useful for both developers and users.
By contrast, internal behaviors are those which are usefull only for developers.
Behavior for a corner case registered in a bug track system is
a good example of internal behaviors.

@@

Since no-parameter properties has no parameters,
it is enough to test them just one.
However, QuickCheck 2.3 or earlier tests no-parameter properties 100 times.
More precisely, the evaluation results are memorized and they are
compared with {\tt True} 100 times.
The current maintainer of QuickCheck modified that
no-parameter properties are tested just once in its source repository.

>>>>

We can categorize behaviors into two types: visible behaviors
and internal behaviors.
Visible behaviors are those which are useful for both developers and users.
By contrast, internal behaviors are those which are usefull only for developers.
A good example of internal behaviors
is behavior for a corner case registered in a bug track system.

@@

Since no-parameter properties have no parameters,
it is enough to test them just one.
However, QuickCheck 2.3 or earlier tests no-parameter properties 100 times.
More precisely, the evaluation results are memorized and they are
compared with {\tt True} 100 times.
The current maintainer of QuickCheck modified that
no-parameter properties are tested just once in its source repository.
